Rule Synthesis for Rule-based Intrusion Detectors

### 2020-06-02 paper/paper.tex
pass on related work

This section elaborates on the most similar work.

%We discuss in the following techniques similar in goal to ours. Unfortunately

@@

\textbf{Alternative methods for rule synthesis.} As detailed before,
we could not access the tools implementing the techniques for
comparison. Nevertheless, we found that there are important

@@

considered. Guruprasad \etal{}\cite{guruprasad} also proposes an
evolutionary framework, creating their own ICMP dataset as Vollmer,
but also using DARPA 1999 \cite{darpa1999} and ISCX 2012 \cite{iscx}
datasets for non-ICMP attacks. Although Guruprasad supports more
protocols than Vollmer, our approach still supports a larger set of
protocols and the ability to ranks rules. Muthuregunathan
\etal{}~\cite{muthuregunathan-etal2009} propose a clustering method to
create rules. They characterize candidate solutions as a set of field
values and use a clustering algorithm---hybrid k-means partitioned
around menoids---to isolate malicious from benign
traffic. Subsequently, they optimize the formed clusters using genetic
algorithms and hill-climbing search. Ou approach differs from theirs
in the method used, results, and support for content
options. Kao~\etal~\cite{Kao2015AutomaticNR} proposed ARGS, a system
to synthesize http rules that take malicious traffic as input. ARGS
looks for a common pattern across the different inputs to define
rules. It does not take existing rules as input or benign

>>>>

This section elaborates on the most similar work to ours.

%We discuss in the following techniques similar in goal to
%ours. Unfortunately

%% As detailed before,
%% we could not access the tools implementing the techniques for
%% comparison. Nevertheless, we found that t

@@

\textbf{Alternative methods for rule synthesis.} There are important

@@

considered. Guruprasad~\etal{}~\cite{guruprasad} also used an
evolutionary approach to solve the problem. Although the solution of
Guruprasad~\etal{} supports more protocols than Vollmer~\etal{}', our
approach still supports a larger set of protocols and the ability to
ranks rules. Muthuregunathan~\etal{}~\cite{muthuregunathan-etal2009}
propose a clustering method to create rules. They characterize
candidate solutions as a set of field values and use a clustering
algorithm---hybrid k-means partitioned around menoids---to isolate
malicious from benign traffic. Subsequently, they optimize the formed
clusters using a genetic algorithm and hill-climbing search. Ou
approach differs from theirs in the method used, results, and support
for content options. Kao~\etal~\cite{Kao2015AutomaticNR} proposed
ARGS, a system to synthesize http rules that take malicious traffic as
input. ARGS looks for a common pattern across the different inputs to
define rules. It does not take existing rules as input or benign
